---
output:
  html_document
---

<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>

<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>


<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>

<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>


<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->

<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 100000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Connect to Data Source, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)

access_raw_tbl <- tbl(conn1, "MV_DM_PATIENT_ACCESS")
                      
```


```{r New Patient Entry Processing, echo = FALSE, warning = FALSE, message = FALSE}

# Analysis based on arrived visits only ---------------------------------------
new_patient_arrived <- access_raw_tbl %>%
  left_join(
    (access_raw_tbl %>%
       # filter(MRN %in% c("15151", "H235951")) %>%
       filter(DERIVED_STATUS_DESC == "Arrived") %>%
       arrange(MRN, APPT_DTTM, APPT_MADE_DTTM) %>%
       group_by(MRN) %>%
       mutate(first_new_visit = row_number()) %>%
       mutate(second_new_visit = APPT_DTTM - lag(APPT_DTTM)) %>%
       mutate(new_patient = ifelse(first_new_visit == 1, 1, ifelse(second_new_visit > 730, 1, 0))) %>%
       ungroup() %>%
       mutate(unique_pt_ID = cumsum(new_patient)) %>%
       group_by(MRN, unique_pt_ID) %>%
       mutate(visit_ID = row_number()) %>%
       ungroup() %>%
       dplyr::select(PAT_ENC_CSN_ID, new_patient, unique_pt_ID, visit_ID)),
    by = "PAT_ENC_CSN_ID") 


# Analysis based on scheduling activities -------------------------------------
# Combined with analysis based on arrived visits only
new_patient_data <- new_patient_arrived %>%
  arrange(MRN, APPT_DTTM, APPT_MADE_DTTM) %>%
  group_by(unique_pt_ID) %>%
  mutate(first_entry_visit = first(APPT_ENTRY_USER_NAME_WID)) %>% # Identify first entry point
  group_by(MRN) %>%
  mutate(first_new_scheduling = row_number()) %>%
  # mutate(second_new_scheduling = difftime(APPT_DTTM, lag(APPT_DTTM), units = "days")) %>%
  mutate(second_new_scheduling = APPT_DTTM - lag(APPT_DTTM)) %>%
  mutate(new_patient_scheduling = ifelse(first_new_scheduling == 1, 1, ifelse(second_new_scheduling > 730, 1, 0))) %>%
  ungroup() %>%
  mutate(unique_pt_ID_scheduling = cumsum(new_patient_scheduling)) %>%
  group_by(MRN, unique_pt_ID_scheduling) %>%
  mutate(scheduling_ID = row_number()) %>%
  group_by(unique_pt_ID_scheduling) %>%
  mutate(first_entry_scheduling = first(APPT_ENTRY_USER_NAME_WID)) %>% # Identify first entry point for scheduling
  ungroup() %>%
  mutate(Appt.Status = case_when(SAME_DAY_CANC_YN == "Y" & DERIVED_STATUS_DESC %in% c("Canceled","Rescheduled","Bumped") ~ paste0("SameDay ",DERIVED_STATUS_DESC),
                                 TRUE ~ DERIVED_STATUS_DESC))

```


```{r Data Filtering, echo = FALSE, warning = FALSE, message = FALSE}

# Filter New Patient Entry Processed Data -----------
data <- new_patient_data %>%
  dplyr::select(MRN, PAT_ENC_CSN_ID, 
                SITE, DEPARTMENT_NAME, DEPT_SPECIALTY_NAME,
                APPT_DTTM, APPT_MADE_DTTM, APPT_CANCEL_DATE, DERIVED_STATUS_DESC, Appt.Status, SCHED_METHOD, APPT_ENTRY_USER_NAME_WID,
                PROV_ID, PROV_NAME_WID,
                new_patient, unique_pt_ID, visit_ID, first_entry_visit,
                new_patient_scheduling, unique_pt_ID_scheduling, scheduling_ID, first_entry_scheduling) %>%
  collect()

invisible(gc())

# Scheduling Method  ------------------
data <- data %>%
  mutate(sched_method_new = case_when(str_detect(APPT_ENTRY_USER_NAME_WID, "MYCHART") ~ "MyMS/FASTPASS",
                                       str_detect(APPT_ENTRY_USER_NAME_WID, "AVAAMO") ~ "Avaamo",
                                       str_detect(APPT_ENTRY_USER_NAME_WID, "STAYWELL") ~ "Consumer Digital",
                                       str_detect(APPT_ENTRY_USER_NAME_WID, "ASAP") ~ "DocASAP",
                                       str_detect(APPT_ENTRY_USER_NAME_WID, "KYRUUS") ~ "Google",
                                       str_detect(APPT_ENTRY_USER_NAME_WID, "API, OSCAR") ~ "Oscar",
                                       str_detect(APPT_ENTRY_USER_NAME_WID, "ZOCDOC") ~ "ZocDoc",
                                       TRUE ~ "Entry Person"))



# ZocDoc vs. Other Entry ----------------
data <- data %>%
  mutate(first_entry_visit_new = case_when(str_detect(first_entry_visit, "MYCHART") ~ "MyMS/FASTPASS",
                                       str_detect(first_entry_visit, "AVAAMO") ~ "Avaamo",
                                       str_detect(first_entry_visit, "STAYWELL") ~ "Consumer Digital",
                                       str_detect(first_entry_visit, "ASAP") ~ "DocASAP",
                                       str_detect(first_entry_visit, "KYRUUS") ~ "Google",
                                       str_detect(first_entry_visit, "API, OSCAR") ~ "Oscar",
                                       str_detect(first_entry_visit, "ZOCDOC") ~ "ZocDoc",
                                       TRUE ~ "Entry Person"))

data <- data %>%
  mutate(first_entry_scheduling_new = case_when(str_detect(first_entry_scheduling, "MYCHART") ~ "MyMS/FASTPASS",
                                       str_detect(first_entry_scheduling, "AVAAMO") ~ "Avaamo",
                                       str_detect(first_entry_scheduling, "STAYWELL") ~ "Consumer Digital",
                                       str_detect(first_entry_scheduling, "ASAP") ~ "DocASAP",
                                       str_detect(first_entry_scheduling, "KYRUUS") ~ "Google",
                                       str_detect(first_entry_scheduling, "API, OSCAR") ~ "Oscar",
                                       str_detect(first_entry_scheduling, "ZOCDOC") ~ "ZocDoc",
                                       TRUE ~ "Entry Person"))


data <- data %>% 
  mutate(specialty = case_when(DEPT_SPECIALTY_NAME %in% c("Family Medicine", "Internal Medicine") ~ "Primary Care",
                               DEPT_SPECIALTY_NAME %in% c("OB/Gyn", "Obstetrics", "Gynecology") ~ "Ob/Gyn",
                               str_detect(DEPT_SPECIALTY_NAME, "Peds|Pediatric") ~ "Pediatrics",
                               TRUE ~ DEPT_SPECIALTY_NAME))


data <- data %>%
  mutate(Appt.MonthYear = format(as.Date(APPT_DTTM), "%Y-%m"),
         Appt.Year = format(as.Date(APPT_DTTM), "%Y"),
         Appt.Made.MonthYear = format(as.Date(APPT_MADE_DTTM), "%Y-%m"),
         Appt.Made.Year = format(as.Date(APPT_MADE_DTTM), "%Y")) %>%
  group_by(unique_pt_ID) %>%
  mutate(first_visit_year = Appt.Year[new_patient == 1],
         first_visit_monthyear = Appt.MonthYear[new_patient == 1],
         first_visit_site = SITE[new_patient == 1],
         first_visit_specialty = specialty[new_patient == 1]) 


data <- data %>%
  mutate(Appt.Status = case_when(SAME_DAY_CANC_YN == "Y" & DERIVED_STATUS_DESC %in% c("Canceled","Rescheduled","Bumped") ~ paste0("SameDay ",DERIVED_STATUS_DESC),
                                 TRUE ~ DERIVED_STATUS_DESC))

```


```{r}
# 
# invisible(gc())
# 
saveRDS(data, "new_pt_data_01242024.rds")

data <- readRDS("new_pt_data_01242024.rds")

data <- data %>%
  mutate(Appt.MonthYear = format(as.Date(APPT_DTTM), "%Y-%m"))

new_2022 <- data %>%
  filter(first_visit_year == 2022) %>%
  filter(new_patient == 1) %>%
  dplyr::select(PAT_ENC_CSN_ID, MRN, SITE, DEPARTMENT_NAME, APPT_DTTM, PROV_NAME_WID, sched_method_new)

require(openxlsx)
write.xlsx(new_2022, "MSHS Net New Patients_2022.xlsx")
```


```{r Provider Digital Status and Capacity, echo = FALSE, warning = FALSE, message = FALSE}

invisible(gc())

provider_digital_enabled <- data %>%
  group_by(PROV_NAME_WID, PROV_ID, DEPARTMENT_NAME) %>%
  summarise(first_ZocDoc = as.Date(min(APPT_DTTM[Appt.Status == "Arrived" & sched_method_new == "ZocDoc"])),
            last_ZocDoc = as.Date(max(APPT_DTTM[Appt.Status == "Arrived" & sched_method_new == "ZocDoc"])),
            first_findadoc =  as.Date(min(APPT_DTTM[Appt.Status == "Arrived" &  APPT_ENTRY_USER_NAME_WID == "APP, FINDADOC [MSHSFAD]"])),
            last_findadoc =  as.Date(max(APPT_DTTM[Appt.Status == "Arrived" &  APPT_ENTRY_USER_NAME_WID == "APP, FINDADOC [MSHSFAD]"])))

provider_digital_enabled <- provider_digital_enabled %>%
  mutate(ZocDoc_enabled = ifelse(is.infinite(first_ZocDoc), "N", "Y"),
         findadoc_enabled = ifelse(is.infinite(first_findadoc), "N", "Y"))


provider_data <- data %>%
  group_by(PROV_NAME_WID, PROV_ID, VISIT_PROV_STAFF_RESOURCE_C, SITE, specialty, DEPARTMENT_NAME, 
           Appt.Made.Year, Appt.Made.MonthYear, Appt.Year, Appt.MonthYear, sched_method_new, Appt.Status, VISIT_GROUP_NUM) %>%
  summarise(total = n(),
            net_new_pts = sum(new_patient))

provider_data <- left_join(provider_data, provider_digital_enabled)

provider_data <- provider_data %>%
  mutate(enable_status = case_when(ZocDoc_enabled == "Y" & findadoc_enabled == "Y" ~ "Both Enabled",
                                   ZocDoc_enabled == "Y" & findadoc_enabled == "N" ~ "ZocDoc Enabled",
                                   ZocDoc_enabled == "N" & findadoc_enabled == "Y" ~ "FindaDoc Enabled",
                                   TRUE ~ "Not Enabled"))

enabled_status <- provider_data %>%
  group_by(Appt.MonthYear = sum)


```

