---
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>

<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>


<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>

<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>


<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->

<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```



```{r Arrived Net New Patients and Entry Points, echo = FALSE, warning = FALSE, message = FALSE}

# Net new patients & unique MRNs ------------------------
net_new_pts <- data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  group_by(Appt.Year) %>%
  summarise(total_pts = length(unique(MRN)),
            net_new_pts = sum(new_patient))


net_new_pts_site <- data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  group_by(Appt.Year, SITE) %>%
  summarise(total_pts = length(unique(MRN)),
            net_new_pts = sum(new_patient))


net_new_pts_specialty <- data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  group_by(Appt.Year, specialty) %>%
  summarise(total_pts = length(unique(MRN)),
            net_new_pts = sum(new_patient))


# Net new patient count by site and specialty
net_new_pts_site_specialty <- data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  group_by(Appt.Year, first_visit_site, first_visit_specialty) %>%
  summarise(net_new_pts = sum(new_patient))


# Net new patient entry point breakdown --------------------
net_new_pts_entry <- data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  group_by(Appt.Year, SITE, specialty, first_entry_visit_new) %>%
  summarise(net_new_pts = sum(new_patient)) 


# Stickiness -----------------------------------------------
net_new_pts_stick <- data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  group_by(first_visit_year, first_visit_site, first_visit_specialty, first_entry_visit_new, visit_ID) %>%
  summarise(net_new_pts = length(unique(unique_pt_ID)))
  


# Subsequent visits ---------------------------------------- 
net_new_pts_subsequent_visit <- data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  group_by(first_visit_year, first_visit_site, first_visit_specialty, first_entry_visit_new, sched_method_new) %>%
  summarise(net_new_pts = sum(new_patient),
            subsequent_visits = length(unique(PAT_ENC_CSN_ID[visit_ID > 1])),
            subsequent_unique_pts = length(unique(MRN[visit_ID > 1])))


net_new_pts_subsequent_visit_visit_ID <- data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  group_by(first_visit_year, first_visit_site, first_visit_specialty, first_entry_visit_new, sched_method_new, visit_ID) %>%
  summarise(net_new_pts = sum(new_patient),
            subsequent_visits = length(unique(PAT_ENC_CSN_ID[visit_ID > 1])),
            subsequent_unique_pts = length(unique(MRN[visit_ID > 1])))




```



```{r}

net_new_pts_subsequent_visit <- data %>%
  filter(DERIVED_STATUS_DESC == "Arrived") %>%
  group_by(first_visit_year, first_visit_site, first_visit_specialty, first_entry_visit_new, SITE, specialty) %>%
  summarise(net_new_pts = sum(new_patient),
            subsequent_visits = length(unique(PAT_ENC_CSN_ID[visit_ID > 1])),
            subsequent_unique_pts = length(unique(MRN[visit_ID > 1])))


subsequent_visit_specialty <- net_new_pts_subsequent_visit %>% filter(first_visit_year == 2022) %>% group_by(first_visit_specialty, specialty) %>% summarise(total_subsequent = sum(subsequent_visits)) %>%
  group_by(first_visit_specialty) %>%
  mutate(perc = round(total_subsequent/sum(total_subsequent),2))


```


```{r}

bookings <- data %>%
  group_by(Appt.Year, sched_method_new) %>%
  # group_by(Appt.Year, SITE, specialty, sched_method_new, DERIVED_STATUS_DESC) %>%
  summarise(total_scheduling = n(),
            net_new_pts = sum(new_patient))

zocdoc_bookings <- data %>% 
  ungroup() %>%
  filter(Appt.Year, sched_method_new) %>%
  summarise(total = n())

```



```{r Export Data, echo = FALSE, warning = FALSE, message = FALSE}


data_list <- list("net_new_pts" = net_new_pts,
                  "net_new_pts_site" = net_new_pts_site,
                  "net_new_pts_specialty" = net_new_pts_specialty,
                  "net_new_pts_site_specialty" = net_new_pts_site_specialty,
                  "net_new_pts_entry" = net_new_pts_entry,
                  "net_new_pts_stick" = net_new_pts_stick,
                  "net_new_pts_subsequent_visit" = net_new_pts_subsequent_visit)

require(openxlsx)
write.xlsx(data_list, "Net_New_Analysis.xlsx")


invisible(gc())
```


