---
output:
  html_document
---

<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>

<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>


<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>

<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>


<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->

<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Connect to Data Source, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)

access_raw_tbl <- tbl(conn1, "MV_DM_PATIENT_ACCESS")
                      
```


```{r New Patient Entry Processing, echo = FALSE, warning = FALSE, message = FALSE}

# Analysis based on arrived visits only ---------------------------------------
new_patient_arrived <- access_raw_tbl %>%
  # filter(MRN %in% c("15151", "H235951")) %>%
  # mutate(sched_method_new = ifelse("FastPass" %like% "FASTPASS",
  #                                  ifelse(SCHED_METHOD %like% "On My Way", "OnMyWay",
  #                                         ifelse(SCHED_METHOD %like% "Epic Open Scheduling", "Findadoc",
  #                                                ifelse(APPT_ENTRY_USER_NAME_WID %like% "FINDADOC", "Findadoc",
  #                                                       ifelse(APPT_ENTRY_USER_NAME_WID %like% "AVAAMO", "Avaamo",
  #                                                              ifelse(APPT_ENTRY_USER_NAME_WID %like% "STAYWELL", "Consumer Digital",
  #                                                                     ifelse(APPT_ENTRY_USER_NAME_WID %like% "ASAP", "DocASAP",
  #                                                                            ifelse(APPT_ENTRY_USER_NAME_WID %like% "KYRUUS", "Google",
  #                                                                                   ifelse(APPT_ENTRY_USER_NAME_WID %like% "API, OSCAR", "Oscar",
  #                                                                                          ifelse(APPT_ENTRY_USER_NAME_WID %like% "ZOCDOC", "ZocDoc", NA))))))))))) %>%
  # collect()
  # mutate(sched_method_new = ifelse(is.na(sched_method_new) & APPT_ENTRY_USER_NAME_WID %like% "MYCHART", "MyMS",
  #                                  ifelse(is.na(sched_method_new), "Entry Person", sched_method_new))) %>%
  left_join(
    (access_raw_tbl %>%
       # filter(MRN %in% c("15151", "H235951")) %>%
       filter(DERIVED_STATUS_DESC == "Arrived") %>%
       arrange(MRN, APPT_DTTM) %>%
       group_by(MRN) %>%
       mutate(first_new_visit = row_number()) %>%
       mutate(second_new_visit = APPT_DTTM - lag(APPT_DTTM)) %>%
       mutate(new_patient = ifelse(first_new_visit == 1, 1, ifelse(second_new_visit > 730, 1, 0))) %>%
       ungroup() %>%
       mutate(unique_pt_ID = cumsum(new_patient)) %>%
       group_by(MRN, unique_pt_ID) %>%
       mutate(visit_ID = row_number()) %>%
       ungroup() %>%
       dplyr::select(PAT_ENC_CSN_ID, new_patient, unique_pt_ID, visit_ID)),
    by = "PAT_ENC_CSN_ID") 


# Analysis based on scheduling activities -------------------------------------
# Combined with analysis based on arrived visits only
new_patient_data <- new_patient_arrived %>%
  # dplyr::select(MRN, PAT_ENC_CSN_ID, APPT_DTTM, CONTACT_DATE,
  #               APPT_MADE_DTTM, DERIVED_STATUS_DESC,  SCHED_METHOD, APPT_ENTRY_USER_NAME_WID, new_patient, unique_pt_ID, visit_ID) %>%
  arrange(MRN, APPT_DTTM) %>%
  group_by(unique_pt_ID) %>%
  mutate(first_entry_visit = first(APPT_ENTRY_USER_NAME_WID)) %>% # Identify first entry point
  group_by(MRN) %>%
  mutate(first_new_scheduling = row_number()) %>%
  # mutate(second_new_scheduling = difftime(APPT_DTTM, lag(APPT_DTTM), units = "days")) %>%
  mutate(second_new_scheduling = APPT_DTTM - lag(APPT_DTTM)) %>%
  mutate(new_patient_scheduling = ifelse(first_new_scheduling == 1, 1, ifelse(second_new_scheduling > 730, 1, 0))) %>%
  ungroup() %>%
  mutate(unique_pt_ID_scheduling = cumsum(new_patient_scheduling)) %>%
  group_by(MRN, unique_pt_ID_scheduling) %>%
  mutate(scheduling_ID = row_number()) %>%
  group_by(unique_pt_ID_scheduling) %>%
  mutate(first_entry_scheduling = first(APPT_ENTRY_USER_NAME_WID)) %>% # Identify first entry point for scheduling
  ungroup() 
  # dplyr::select(MRN, PAT_ENC_CSN_ID, APPT_DTTM, APPT_MADE_DTTM, DERIVED_STATUS_DESC, SCHED_METHOD, APPT_ENTRY_USER_NAME_WID, 
  #               new_patient, unique_pt_ID, visit_ID, first_entry_visit,
  #               new_patient_scheduling, unique_pt_ID_scheduling, scheduling_ID, first_entry_scheduling,
  #               SITE,  DEPT_SPECIALTY_NAME, DEPARTMENT_NAME) 

```


```{r Data Collect, echo = FALSE, warning = FALSE, message = FALSE}

data <- new_patient_data %>%
  # mutate(year = year(CONTACT_DATE)) %>%
  # filter(year >= 2022) %>%
  dplyr::select(MRN, PAT_ENC_CSN_ID, APPT_DTTM, APPT_MADE_DTTM, DERIVED_STATUS_DESC, SCHED_METHOD, APPT_ENTRY_USER_NAME_WID, 
                new_patient, unique_pt_ID, visit_ID, first_entry_visit,
                new_patient_scheduling, unique_pt_ID_scheduling, scheduling_ID, first_entry_scheduling) %>%
  collect()



# data_2022 <- new_patient_data %>%
#   mutate(year = year(CONTACT_DATE)) %>%
#   filter(year >= 2022) %>%
#   dplyr::select(PAT_ENC_CSN_ID, 
#                 new_patient, unique_pt_ID, visit_ID, first_entry_visit,
#                 new_patient_scheduling, unique_pt_ID_scheduling, scheduling_ID, first_entry_scheduling) %>%
#   collect()
#   




# 
# require(openxlx)
# write_xlsx(test, "Zocdoc data processing sample.xlsx")
  
```


```{r Write Table to Oracle, echo = FALSE, warning = FALSE, message = FALSE}

# #Establish Oracle Cloud connection
# conn3 <- dbConnect(odbc(), "OAO Cloud DB SoYoun",
#                   uid = "KWEONS01",
#                   pwd = "wEKMQpqm22*dvM")
#  
# 
# 
# new_patients <- tbl(conn3, "NEW_PATIENTS")
# new_patients_pull_all <- new_patients %>%
#   collect()
# 
# new_patients_pull_all <- new_patients_pull_all %>%
#   distinct()
# 
# data_remaining <- anti_join(data, new_patients_pull_all)
# 
# 
# batch_size <- 1000
#  
# index_squence <- seq(1, nrow(data_remaining), by = batch_size)
#  
# for (i in index_squence) {
#   if(i == max(index_squence)) {
#     batch <- data_remaining[i:nrow(data_remaining), ]
#   } else {
#     batch <- data_remaining[i:(i + batch_size - 1), ]
#   }
# 
#   dbWriteTable(conn = conn3, name = "NEW_PATIENTS", value = batch, row.names = FALSE, append = TRUE)
#   
#   print(paste0("i is:", i))
#   # print(batch)
# }

```
